An Information Theoretic Formalism \\for Intent Disambiguation

### 2019-01-28 TexStuff/IROS2018_ResubmitTex/GopinathArgall_IROS2019_2.tex
IROS 2019 commit 1. incorporated human model into forward projection.

\documentclass[conference]{IEEEtran}
\usepackage{times}
% numbers option provides compact numerical references in the text. 
\usepackage[numbers]{natbib}
\usepackage{multicol}
\usepackage{tabularx}
\usepackage[bookmarks=true]{hyperref}
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{graphicx}
\usepackage[numbers]{natbib}
\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}
\usepackage{amsmath,amssymb,latexsym,float,epsfig,subfigure}
\usepackage{amsmath} % assumes amsmath package installed  % assumes amsmath package installed
\usepackage{mathtools, bbm}
\usepackage{lipsum}
\usepackage[export]{adjustbox}
\usepackage[normalem]{ulem} % underline
\usepackage{wrapfig}
\usepackage{multirow}
\usepackage{balance}
\usepackage{color}
\usepackage{url}
\usepackage{booktabs}
\usepackage{pifont}
\usepackage{algorithm, algorithmic}
\DeclareMathOperator*{\argmax}{argmax}
%\newcommand{\argmax}{\arg\!\max}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
%\def\bibfont{\footnotesize}
\pdfinfo{
	/Author (Deepak Gopinath, Brenna D. Argall)
	/Title  (Information Theoretic Formulation of Intent Disambiguation)
	/CreationDate (January 31 2018)
	/Subject (Robots)
	/Keywords (Robots)
}
% numbers option provides compact numerical references in the text.

@@

\begin{abstract}
The effectiveness of assistive robots is closely related to their ability to infer the user's needs and intentions \textit{unambiguously} and provide appropriate assistance quickly and accurately. In this paper, we formulate the problem of intent disambiguation in information theoretic terms.  We propose two different methods for intent disambiguation using the information theoretic concepts of \textit{entropy} and \textit{KL divergence}. The proposed algorithms characterize the disambiguation capabilities of the system through the forward projection of probability distributions over goals, utilizing an intent inference scheme and a kinematics model, and computing the average information gain and content. Previous studies have shown that the success of a disambiguation algorithm depends on a variety of factors and parameters. To thoroughly investigate the impact of these various components, we present results from an extensive simulation-based study for both a point robot and physics-based simulation of a six degrees-of-freedom (DoF) robotic arm. Our results indicate that, compared to a baseline, the proposed disambiguation algorithms do facilitate faster intent disambiguation, which in turn allows autonomy assistance to step in earlier during task execution. Additionally, we find that goal inference is more accurate and the total amount of time assistance is engaged is higher.
\end{abstract}

@@

Our insight is that, at any given time, there is a specific set of control modes that are more informative \textit{for} the autonomy than others. Therefore, by having the human provide control input within these information-rich modes, the possibility of inferring the human's intent accurately and unambiguously is increased. This, in turn, allows the autonomy to step in and \textit{assist the human achieve their desired goal earlier}.  This is important, because when the intent inference mechanism infers the incorrect goal (or is simply too slow), the user and autonomy often end up competing instead of collaborating. This can decrease user satisfaction and result in significantly worse performance than either the human or autonomy would produce on their own. In this paper, we address the problem of accurate intent inference by characterizing control modes according to the information content, and proposing a mode switch assistance paradigm that selects the control mode in which a user-initiated motion will \textit{maximally disambiguate} their intent. We formalize the problem of intent disambiguation within the framework of information theory. Specifically, we make use of the information theoretic notions of entropy and Kullback-Leibler (KL) divergence to characterize and quantify the information content---with respect to intent disambiguation---of each control mode.

@@

Our aim is to develop a metric that will capture the ``disambiguation capability'' of a control dimension/mode. Subsequent user operation of the robot in the control mode with maximum disambiguation capability will likely help the system to perform better intent inference and may result in the autonomy providing more appropriate assistance.

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{times}
% numbers option provides compact numerical references in the text. 
\usepackage{changes}
\usepackage[numbers]{natbib}
\usepackage{multicol}
\usepackage{tabularx}
\usepackage[bookmarks=true]{hyperref}
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{graphicx}
\usepackage[numbers]{natbib}
\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}
\usepackage{amsmath,amssymb,latexsym,float,epsfig,subfigure}
\usepackage{amsmath} % assumes amsmath package installed  % assumes amsmath package installed
\usepackage{mathtools, bbm}
\usepackage{lipsum}
\usepackage[export]{adjustbox}
\usepackage[normalem]{ulem} % underline
\usepackage{wrapfig}
\usepackage{multirow}
\usepackage{balance}
\usepackage{color}
\usepackage{url}
\usepackage{booktabs}
\usepackage{pifont}
\usepackage{algorithm, algorithmic}
\DeclareMathOperator*{\argmax}{argmax}
%\newcommand{\argmax}{\arg\!\max}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
%\def\bibfont{\footnotesize}
\pdfinfo{
	/Author (Deepak Gopinath, Brenna D. Argall)
	/Title  (Information Theoretic Formulation of Intent Disambiguation)
	/CreationDate (January 31 2018)
	/Subject (Robots)
	/Keywords (Robots)
}
% numbers option provides compact numerical references in the text.

@@

\begin{abstract}
The effectiveness of assistive robots is closely related to their ability to infer the user's needs and intentions \textit{unambiguously} and provide appropriate assistance quickly and accurately. \added{In this paper, we proposed a mode selection paradigm that enhances autonomy's intent inference capabilities by exploiting the fact that how the human operates the robot and reveals his/her intent is conditioned on the current control mode. We formulate this as a problem of intent disambiguation in information theoretic terms. }In this paper, we formulate the problem of intent disambiguation in information theoretic terms.  We propose two different methods for intent disambiguation using the information theoretic concepts of \textit{entropy} and \textit{KL divergence}. The proposed algorithms characterize the disambiguation capabilities of the \added{different control modes?} system through the forward projection of probability distributions over goals, utilizing an intent inference scheme and a kinematics model, and computing the average information gain and content. Previous studies have shown that the success of a disambiguation algorithm depends on a variety of factors and parameters. To thoroughly investigate the impact of these various components, we present results from an extensive simulation-based study for both a point robot and physics-based simulation of a six degrees-of-freedom (DoF) robotic arm. Our results indicate that, compared to a baseline, the proposed disambiguation algorithms do facilitate faster intent disambiguation, which in turn allows autonomy assistance to step in earlier during task execution. Additionally, we find that goal inference is more accurate and the total amount of time assistance is engaged is higher.
\end{abstract}

@@

Our insight is that, at any given time, there is a specific set of control modes that are more informative \textit{for} the autonomy than others. Therefore, by having the human provide control input within these information-rich modes, the possibility of inferring the human's intent accurately and unambiguously is increased. \added{Talk about this specifically in terms of how mode selection can improve intent inference. }This, in turn, allows the autonomy to step in and \textit{assist the human achieve their desired goal earlier}.  This is important, because when the intent inference mechanism infers the incorrect goal (or is simply too slow), the user and autonomy often end up competing instead of collaborating. This can decrease user satisfaction and result in significantly worse performance than either the human or autonomy would produce on their own. In this paper, we address the problem of accurate intent inference by characterizing control modes according to the information content, and proposing a mode switch assistance paradigm that selects the control mode in which a user-initiated motion will \textit{maximally disambiguate} their intent. We formalize the problem of intent disambiguation within the framework of information theory. Specifically, we make use of the information theoretic notions of entropy and Kullback-Leibler (KL) divergence to characterize and quantify the information content---with respect to intent disambiguation---of each control mode.

@@

\added{Rewrite this section in terms of math of Bayesian inference. And don't talk about need for intent disambiguation, but instead make a case for how inference can be affected by the control mode.Write basic equation. Under the constrain that user can only operate the robot in one mode at a time rewrite the equation conditioned on mode. Isolate the likelihood and explain the meaning of it. And how the fact that the likelihood differs for different modes can be exploited to come up with a mode selection paradigm. To characterize which one is good we use information gain and entropy measures. Check out Siddarths paper for recursive bayesian formulation. This is general to any recursive situation. Talk about human following a policy that noisily optimizes shortest distance in Cartesian space. Talk about counterfactual reasoning? That is, we are asking the question what if, the human operated in so and so mode, how would the probabilities update.}
Our aim is to develop a metric that will capture the ``disambiguation capability'' of a control dimension/mode. Subsequent user operation of the robot in the control mode with maximum disambiguation capability will likely help the system to perform better intent inference and may result in the autonomy providing more appropriate assistance.
